\documentclass[10pt,letterpaper]{resume/resume}

\usepackage{paralist}
\usepackage{multicol}
\usepackage[english]{babel}

\definecolor{rulestartcolor}{rgb}{0.6, 0.6, 1}
\definecolor{ruleendcolor}{rgb}{0.6, 1, 0.6}

\begin{document}
  \begin{minipage}[t]{\linewidth * 1 / 3}
    {\Large Gilles BESAN\c{C}ON}\\
      \begin{tabular}{c l}
         \email{&gilles.besancon@gmail.com}\\
         \phone{&+44 7479 930982}\\
      \end{tabular}
  \end{minipage}
  \begin{minipage}[t]{\linewidth * 2 / 3}
    \begin{center}
      {\huge{Senior Software Engineer\\Architecture \& Design\\Java, Eclipse RCP, C, C++, C\#}}
      \begin{tabular}{c l c l c l}
      \french{French:&Native}&\englishus{English:&Fluent}&\spanish{Spanish:&Conversational}\\
      \end{tabular}
    \end{center}
  \end{minipage}
  
  \begin{minipage}[t]{\linewidth}
    \section{Technical Skills}
    \begin{tabular}{ll}
	Operating Systems&Windows, GNU/Linux, Mac OS X\\
	Methodologies&UML, Agile, Kanban, CMMI\\
	Java&Eclipse, OSGi, Eclipse RCP, IDL, JNI, JNA, JProfiler, JUnit, JAXB, Gradle, Maven, ANT\\
	Java UI&AWT/Swing, SWT/JFace, JavaFX, Ilog JViews Chart\\
	Java Modeling&EMF, EEF, EGF, Acceleo, ATL, XText\\
	C/C++/C\#&Microsoft Visual Studio, Cuda, NUnit, NCover\\
%	C/C++/C\# UI&Ilog Views, OpenInventor, Qt, DirectX\\
	Web&JavaScript, Polymer\\
	Source Control Manager&Git, SVN, CVS, TFVC, OmniWorks\\
	Tools&Jira, MantisBT, Hudson/Jenkins, TFS/VSTS, GitLab, Sonar, Google Cloud Platform\\
%	IPhone/Android&Objective-C, IPhone SDK, X-Code, Android SDK, ADT\\
    \end{tabular}
  \end{minipage}
  
  \begin{minipage}[t]{\linewidth}
    \section{Work Experience}

\job[Senior Software Engineer]{Schlumberger WesternGeco - Gatwick - U.K.}{November 2013 to \ldots}

\assignment[AI Planning]{Schlumberger WesternGeco - Gatwick - U.K.}{May 2016 to \ldots}
\par Implementation in java of a state of the art AI planner for industrial applications.
\par Use of Visual Studio Team Services for Project Management, Build and Continuous deployment to Google Cloud Platform using Docker.
\par\underline{Environment:} Windows, CentOS, VSTS, Git, Java, Gradle, SpringBoot, Polymer, Docker, Google Cloud Platform

\assignment[Omega Platform]{Schlumberger WesternGeco - Gatwick - U.K.}{January 2016 to April 2017}
\par Lead a team of 2 engineers to manage and maintain the build of the multi-platform Geophysical Data Processing Platform Omega. 
\par Clean and organize the development infrastructure (Virtual Machine, Source Control Manager). 
\par Analyze the development, test, deployment process and implement improvements.
\par Manage the build and packaging of the annual release of the Omega Platform and daily/weekly patches.
\par\underline{Environment:} Windows, CentOS, TFS, Jenkins, GitLab, Gitolite, OmniWorks, Git, UML
%
%\assignment[Omega Platform]{Schlumberger WesternGeco - Gatwick - U.K.}{July 2015 to January 2016}
%\par Analysis of the Geophysical Data Processing Platform Omega, to identify weakness of the product.
%\par Contribute to plan the sustenance and improvement of the system regarding its architecture, design and work methodologies.
%\par\underline{Environment:} CentOS, C++, Java, CORBA, JacORB, Git, Google Cloud
%
%\assignment[OilSim]{Schlumberger NeXT - Gatwick - U.K.}{November 2014 to July 2015}
%\par I reinforced the team developing the web-based training simulator OilSim (http://www.oilsim.com)
%\par Advise and set up improvement of methods and tools to be used on the project based on agile methodology principles.
%\par Involved in the Design \& Implementation of synthetic survey generator using DirectX (Direct3D and Direct2D) based off-screen rendering.
%\par\underline{Environment:} Windows, UML, Microsoft Visual Studio, TFS, HTML5, PHP, JavaScript, C++, DirectX

\job[Software Engineer Trainee - Visa J-1]{Schlumberger WesternGeco - Houston,TX - U.S.A.}{April 2013 to September 2014}
\par In the context of a cultural exchange between France and the U.S.A., I joined an existing team developing a plugin for Petrel.
\par Specification, Design, Implementation \& Recurent Demos to the users of new survey design and modeling features.
\par Enhance maintainability of code by doing strong refactoring (defining patterns, removing duplicate)
\par\underline{Environment:} Windows, UML, Microsoft Visual Studio, TFS, C\#, C++/CLI, C++, Ocean API, OpenInventor, NUnit, NCover, SCRUM

\job[Software Architecture \& Design Engineer Consultant]{Apside - Brest - France}{August 2006 to March 2013}

\assignment[Electronic Warfare Tools]{THALES Airborne Systems - Brest - France}{October 2011 to March 2013}
\par In the context of a collaborative research project including THALES and 2 Research Labs from Brest (ENSTA and Telecom Bretagne), whose goal is to generate drivers code from data and behaviour model of interfaces.
\par Architecture, Design \& Implementation of a Modelling Tool based on Eclipse Modeling Framework to design data interfaces, generate Documentation, Ada - C - VHDL code and configuration file for data analysis tools (Network, VME Bus).
\par\underline{Environment:} Windows, Red Hat, Ada, C, VHDL, HTML, Eclipse RCP, EMF, EEF, EGF, Acceleo, ATL, XText, Hudson

\assignment[Electronic Warfare Mission Debriefing Tool]{THALES Airborne Systems - Brest - France}{August 2008 to July 2011}
\par In the context of a partnership between Apside and THALES, I was in charge for managing a team of 5 to 8 engineers.
\par Architecture, Design \& Implementation of a new Mission Debriefing Tool Framework based on Eclipse RCP Framework to replace existing C++ Mission Debriefing Tool Framework.
\par\underline{Environment:} Windows, Red Hat, UML, Eclipse RCP, Ilog JViews Chart, JProfiler, JNI, Ant, SVN, Mantis
%
%\assignment[Customer service IPhone application framework]{Orange Labs - Lannion - France}{March 2010 to April 2010}
%\par Architecture, Design \& Implementation of a massively customizable application framework for customer services (interactive avatar, geolocalisation, voice recognition, vocalisation and text based chat) 
%\par\underline{Environment:} Mac OS X, X-Code, Objective-C, C, IPhone SDK, SCRUM

\assignment[Satellite mission planning software]{THALES Airborne Systems - Brest - France}{January 2008 to August 2008}
\par Architecture, Design \& Implementation of an Eclipse RCP based application from an existing C application.
\par\underline{Environment:} Windows, Red Hat, UML, Eclipse RCP, Java, JNI, C, CVS

\assignment[Electronic Warfare Mission Debriefing Tools]{THALES Airborne Systems - Brest - France}{August 2006 to August 2008}
\par Design \& Implementation of maintenance and major improvments for multiple electronic warfare mission debriefing tools based on a common framework.
\par\underline{Environment:} Windows, Microsoft Visual Studio C++, C/C++, Ilog Views, JNI, CVS
%
%\job[Research internship]{UBO - Brest - France}{February 2006 to June 2006}
%\par Optimization of a Multi-Agent Physical Engine for Biological Phenomenons simulation using GPU shader \& PPU (SimBioDyn).
%\par\underline{Environment:} Windows, UML, Microsoft Visual Studio C++, OpenGL 2.0, \LaTeX
%
%\job[Industrial internship]{Spacebel - Liège - Belgium}{August 2004 to January 2005}
%\par Investigation of the opportunity to implement satellite hardware simulation software using System-C library.
%\par\underline{Environment:} Windows, Debian, UML, C/C++, System-C
  \end{minipage}

  \begin{minipage}[t]{\linewidth}
    \section{Education}
      \begin{tabularx}{\linewidth}{lX}%
        2006 & Master of sciences of National Engineering School of Brest \hfill ENIB - Brest - France\\ 
        2006 & Research Master of sciences, technologies, health (Major in computer science and telecommunications)\hfill ENIB - Brest - France\\
      \end{tabularx}%
  \end{minipage}

  \vfill
  \begin{center}References available on request\end{center}
\end{document}
